\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Font options
% \usepackage[sfdefault]{roboto}  % Sans-serif font
% \usepackage[sfdefault]{tgheros} % Arial/Helvetica-like font
% \usepackage[sfdefault]{helvet}  % Sans-serif font - Helvetica
\usepackage[sfdefault]{tgheros}  % Arial/Helvetica-like font
\renewcommand{\familydefault}{\sfdefault}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{\Large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]

% Ensure PDF is machine readable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
\vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-7pt}
}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingList}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

% \begin{center}
%   \textbf{\Huge SHOAIB SHAHRIAR} \\
%   \vspace{2pt}
%   +8801723256667 \quad | \quad \href{mailto:shoaibshahriar29@email.com}{shoaibshahriar29@email.com} \quad | \quad 
%   \href{https://linkedin.com/in/biggo29/}{linkedin.com/in/biggo29} \quad | \quad
%   \href{https://github.com/biggo29}{github.com/biggo29} | Dhaka, Bangladesh \quad
% \end{center}

\begin{center}
  \textbf{\Huge SHOAIB SHAHRIAR} \\
  \vspace{2pt}
  +8801723256667 | \href{mailto:shoaibshahriar29@gmail.com}{shoaibshahriar29@gmail.com} | \href{https://linkedin.com/in/biggo29/}{linkedin.com/in/biggo29} | \href{https://github.com/biggo29}{github.com/biggo29} | Dhaka, Bangladesh 
\end{center}

% \section{PROFESSIONAL SUMMARY}
% Lead Software Engineer with 8+ years of experience designing and architecting scalable, event-driven systems and enterprise-grade eCommerce platforms using C\#, ASP.NET Core, and Azure Cloud. Expertise in Microservices, CQRS, Clean Architecture, and Test-Driven Development (TDD), delivering high-quality solutions with 99\%+ test coverage.
\section{PROFESSIONAL SUMMARY}
Lead Software Engineer with 8+ years of experience designing and architecting scalable \textbf{backend services, RESTful APIs, and distributed event-driven systems} powering enterprise-grade eCommerce platforms using C\#, ASP.NET Core, and Azure Cloud. Expertise in Microservices, CQRS, Clean Architecture, Dependency Injection, and Test-Driven Development (TDD), delivering high-quality solutions with 99\%+ test coverage.

Strong background in API architecture, performance optimization, asynchronous programming, and secure backend development (RBAC, GDPR). Actively leveraging \textbf{Agentic AI coding workflows} using GitHub Copilot, Claude, ChatGPT, and Gemini to enhance developer productivity, code quality, and delivery speed.

Proven leadership in guiding cross-functional teams, conducting code reviews, and implementing CI/CD pipelines through Azure DevOps. Recognized for developing award-winning national e-Governance projects, including the WSIS Award 2021-winning CBVMP for BTRC and e-TIN solutions for the National Board of Revenue. Background in competitive programming, ACM-ICPC Dhaka Regional Contests participant (2014--2016).

% \section{TECHNICAL SKILLS}
% \resumeSubHeadingList
%   \resumeItem{\textbf{Programming Languages}: C\#, Java, SQL, JavaScript}
%   \resumeItem{\textbf{Frameworks}: ASP.NET Core, ASP.NET MVC, ASP.NET Web API, CQRS, Clean Architecture, Event-Driven Architecture}
%   \resumeItem{\textbf{Cloud \& DevOps}: Azure Cloud, Azure DevOps, Docker, CI/CD, NServiceBus}
%   \resumeItem{\textbf{Databases \& Reporting Tool}: Microsoft SQL Server, Oracle, MySQL, MS Report Builder, Jasper}
%   \resumeItem{\textbf{Testing \& Logging}: TDD, Unit Testing (XUnit, MSpec), NLog}
%   \resumeItem{\textbf{Architecture \& Documentation}: System Architecture Design, Technical Documentation, Confluence, Draw.io, Azure DevOps Wiki}
%   \resumeItem{\textbf{Leadership}: Agile/Scrum, Code Review, Requirements Analysis, Stakeholder Management, Task Estimation, Ticket Management}
% \resumeSubHeadingListEnd


\section{TECHNICAL SKILLS}
\resumeSubHeadingList
  \resumeItem{\textbf{Programming Languages}: C\#, Java, SQL, JavaScript}
  % \resumeItem{\textbf{Frameworks \& Architecture}: .NET 8, ASP.NET Core, CQRS, Clean Architecture, Event-Driven Architecture}
  % \resumeItem{\textbf{Frameworks \& Architecture}: .NET 8, ASP.NET Core, RESTful APIs, Web API, CQRS, Clean Architecture, Event-Driven Architecture, Dependency Injection, Middleware, Async Programming, Caching (Output Caching), Scheduled Jobs (Cron)}
  % \resumeItem{\textbf{Frameworks \& Architecture}: .NET 8, ASP.NET Core, RESTful APIs, Web API, CQRS, Clean Architecture, Event-Driven Architecture, Dependency Injection, Middleware, Async Programming, Caching (Output Caching), Scheduled Jobs (Cron)}
  \resumeItem{\textbf{Frameworks \& Architecture}: .NET 8, ASP.NET Core, RESTful APIs, Web API, CQRS, Clean Architecture, Event-Driven Architecture, Dependency Injection, Middleware, Async Programming, Caching (Output Caching), Scheduled Jobs (Cron)}
  \resumeItem{\textbf{Data Access}: EF Core, LINQ}
  \resumeItem{\textbf{API \& Security}: Swagger/OpenAPI, JWT, OAuth2, RBAC, Secure API Design}
  % \resumeItem{\textbf{Cloud \& DevOps}: Azure Cloud, Azure DevOps, Docker, CI/CD}
  % \resumeItem{\textbf{Cloud \& DevOps}: Azure Cloud Services, Azure DevOps, Docker, CI/CD, Observability, Logging, Monitoring}
  \resumeItem{\textbf{Cloud \& DevOps}: Azure DevOps, CI/CD Pipeline Design, Docker, Observability, Logging, Monitoring}
  \resumeItem{\textbf{Databases}: Microsoft SQL Server, Oracle, MySQL}
  \resumeItem{\textbf{AI-Assisted Development}: GitHub Copilot, ChatGPT, Claude, Gemini, Prompt Engineering, Agentic AI Workflows}
  \resumeItem{\textbf{Reporting \& Monitoring}: MS Report Builder, ELK Stack (Elasticsearch, Logstash, Kibana), NLog}
  \resumeItem{\textbf{ERP \& Enterprise Systems}: SAP ERP (Foundational Knowledge), Enterprise Resource Planning (ERP) Concepts}
  % \resumeItem{\textbf{Testing \& Quality Assurance}: TDD, Unit Testing (XUnit, MSpec)}
  \resumeItem{\textbf{Testing \& Quality Assurance}: TDD, Unit Testing (XUnit, MSpec), Mocking (Moq)}
  \resumeItem{\textbf{Architecture \& Documentation}: System Architecture Design, Technical Documentation, Confluence, Draw.io, Azure DevOps Wiki}
  \resumeItem{\textbf{Leadership}: Agile/Scrum, Code Review, Requirements Analysis, Stakeholder Management, Task Estimation, Ticket Management}
\resumeSubHeadingListEnd

\section{PROFESSIONAL EXPERIENCE}
\resumeSubHeadingList

\resumeSubheading
  {Lead Software Engineer (Aug 01, 2024 -- Sep 30, 2025)}{}
  {Echologyx Ltd., Dhaka, Bangladesh \textit{(Client: Connect Distribution Services Ltd. / ScrewfixSpares, Kingfisher PLC)}}{}
  \resumeSubHeadingList
    % \resumeItem{Led and mentored a team of 8--10 engineers delivering enhancements to \textbf{eSpares.co.uk}, a high-traffic UK eCommerce platform, achieving 99.9\% unit test covered and 20\% faster deployment cycles using C\#, ASP.NET Core, .NET~8, and Azure DevOps.}
    \resumeItem{Led and mentored a team of 8--10 engineers delivering scalable \textbf{backend services and RESTful APIs} for \textbf{eSpares.co.uk}, a high-traffic UK eCommerce platform, achieving 99.9\% uptime and 20\% faster deployment cycles using C\#, ASP.NET Core, .NET~8, and Azure DevOps.}
    \resumeItem{Owned end-to-end delivery including business analysis, solution architecture, and cross-functional stakeholder alignment, solution design, estimation, and stakeholder alignment with UK business and operations teams.}
    \resumeItem{Guided development across microservices, APIs, and integrations using CQRS, Clean Architecture, TDD (XUnit, MSpec), ensuring 99\%+ test coverage and near-zero post-release defects.}
    \resumeItem{Contributed to both eCommerce and \textbf{Warehouse Management System (WMS)} features, including inventory workflows, reporting, and system integrations supporting UK fulfilment operations.}
    \resumeItem{Authored architecture diagrams, technical documentation, and operational reports using Confluence and Draw.io; enforced RBAC, GDPR compliance, and secure API standards.}
    % \resumeItem{Adopted AI-assisted development workflows using GitHub Copilot, Claude, and ChatGPT to accelerate feature delivery, code reviews, and documentation generation across the engineering team.}
    \resumeItem{Integrated \textbf{Agentic AI development workflows} (GitHub Copilot, Claude, ChatGPT, Gemini) to accelerate backend development, improve code quality, and streamline documentation and engineering productivity.}
  \resumeSubHeadingListEnd

% \vspace{50pt}

\resumeSubheading
  {Senior Software Engineer (Nov 10, 2020 -- Jul 31, 2024)}{}
  {Echologyx Ltd., Dhaka, Bangladesh \textit{(Client: Connect Distribution Services Ltd. / ScrewfixSpares, Kingfisher PLC)}}{}
  \resumeSubHeadingList
    % \resumeItem{Key contributor to the design and evolution of \textbf{eSpares.co.uk}, architecting a UK-based eCommerce platform with 30+ microservices using C\#, ASP.NET Core, CQRS, NServiceBus, and Azure DevOps, supporting 15,000+ daily users and £1M+ monthly sales.}
    \resumeItem{Key contributor to the design and evolution of \textbf{eSpares.co.uk}, architecting scalable backend services and REST APIs across 30+ microservices using C\#, ASP.NET Core, CQRS, NServiceBus, and Azure DevOps, supporting 15,000+ daily users and £1M+ monthly sales.}
    \resumeItem{Improved system performance and reliability through TDD (XUnit, MSpec), achieving 99\% unit test coverage and reducing production defects to near zero.}
    \resumeItem{Delivered business-driven features in collaboration with product, warehouse, and operations teams, translating requirements into scalable backend services and integrations.}
    \resumeItem{Optimized Microsoft SQL Server performance for high-volume workloads, supporting 1M+ products across the UK and Ireland.}
  \resumeSubHeadingListEnd


% \vspace{200pt}


\resumeSubheading
  {Programmer (Dec 23, 2017 -- Nov 04, 2020)}{}
  {Synesis IT PLC, Dhaka, Bangladesh}{}
  \resumeSubHeadingList
    \resumeItem{Key contributor to the WSIS Award-winning Central Biometric Verification Monitoring Platform (CBVMP) for BTRC, integrating with all telecom operators in Bangladesh.}
    \resumeItem{Developed the CBVMP platform using Java, Servlet, and Oracle, enabling biometric verification for 100M+ SIM/MSISDN holders with capacity for 500 TPS (usual 20–50 TPS) and maintaining the longest zero downtime in any e-Governance application in the country.}
    \resumeItem{Developed and integrated real-time log monitoring with Kibana, Elasticsearch, and Logstash, enabling faster issue detection and reducing troubleshooting time.}
    \resumeItem{Designed and enhanced e-TIN solutions and APIs using ASP.NET Core and SQL Server for the National Board of Revenue, integrating with multiple government stakeholders to increase tax compliance and revenue.}
    \resumeItem{Developed SaaS-based e-Governance solutions using Java, C\#, ASP.NET MVC, ASP.NET Core, Oracle, and SQL Server for government and enterprise clients.}
  \resumeSubHeadingListEnd

\resumeSubheading
  {.NET Developer (Jan 17, 2017 -- Dec 21, 2017)}{}
  {RMG Networks, Dallas, TX, USA (Remote)}{}
  \resumeSubHeadingList
    \resumeItem{Built desktop applications for digital signage solutions using C\#, RCF, WCF, and WPF.}
  \resumeSubHeadingListEnd

\resumeSubHeadingListEnd


% \section{PROFESSIONAL EXPERIENCE}
% \resumeSubHeadingList

% \resumeSubheading
%   {Lead Software Engineer (Aug 2024 -- Present)}{}
%   {Echologyx Ltd. Dhaka, Bangladesh}{}
%   \resumeSubHeadingList
%     \resumeItem{Led a team of 8 developers to enhance a microservices-based eCommerce platform using C\#, ASP.NET MVC, ASP.NET Core, .NET 8, Azure DevOps, achieving 99.9\% uptime and 20\% faster deployment cycles.}
%     \resumeItem{Orchestrated requirements analysis, ticket creation, and task distribution using Jira and Azure DevOps, reducing project delivery timelines by 15\%.}
%     \resumeItem{Authored system architecture diagrams and technical documentation in Confluence and Draw.io, improving stakeholder alignment, team collaboration, and cross-team understanding of complex microservices.}
%     \resumeItem{Mentored developers in TDD, XUnit, MSpec, CQRS, Clean Architecture, improving code quality and reducing defects by 25\%.}
%     \resumeItem{Implemented secure API design principles, enforced role-based access control (RBAC), and ensured compliance with GDPR and industry security best practices, aligning the platform with enterprise and regulatory requirements.}
%   \resumeSubHeadingListEnd
    
%     \resumeSubheading
%       {Senior Software Engineer (Nov 2020 -- Jul 2024)}{}
%       {Echologyx Ltd., Dhaka, Bangladesh}{}
%       \resumeSubHeadingList
%         \resumeItem{Architected a scalable UK-based eCommerce platform with 30+ microservices using C\#, ASP.NET Core, CQRS, NServiceBus, and Azure DevOps, supporting 15,000+ daily users and £1M+ monthly revenue.}
%         \resumeItem{Designed feature workflows and system diagrams using Draw.io and Confluence, enhancing cross-team understanding of complex microservices.}
%         \resumeItem{Achieved 99\% test coverage through TDD with XUnit and MSpec, ensuring robust and maintainable codebases.}
%         \resumeItem{Optimized database operations in Microsoft SQL Server for high-traffic systems, handling 1M+ products across the UK and Ireland.}
%   \resumeSubHeadingListEnd

%   \resumeSubheading
%     {Programmer, (Dec 2017 -- Nov 2020)}{}
%     {Synesis IT PLC, Dhaka, Bangladesh}{}
%     \resumeSubHeadingList
%       \resumeItem{Developed SaaS-based e-Governance solutions using Java, C\#, ASP.NET MVC, ASP.NET Core, Oracle, and SQL Server for government and enterprise clients.}
%       \resumeItem{Key contributor to the WSIS Award-winning Central Biometric Verification Monitoring Platform (CBVMP) for BTRC, integrating with all telecom operators in Bangladesh.}
%       \resumeItem{Designed and enhanced e-TIN solutions and APIs for the National Board of Revenue, streamlining taxpayer services nationwide.}
%     \resumeSubHeadingListEnd

%   \resumeSubheading
%     {.NET Developer (Jan 2017 -- Dec 2017)}{}
%     {RMG Networks, Dallas, TX, USA (Remote)}{}
%     \resumeSubHeadingList
%       \resumeItem{Built desktop applications for digital signage solutions using C\#, RCF, WCF, and WPF.}
%     \resumeSubHeadingListEnd
% \resumeSubHeadingListEnd

% \section{KEY PROJECTS}
% \resumeSubHeadingList
%   \resumeSubheading
%     {Scalable UK-Based eCommerce Platform (2021 -- 2024)}{}
%     {Echologyx Ltd. Dhaka, Bangladesh}{}
%     \resumeSubHeadingList
%       \resumeItem{Designed a microservices architecture with 30+ services using C\#, ASP.NET Core, CQRS, and Azure, supporting 15,000+ daily users and £1M+ monthly revenue.}
%       \resumeItem{Achieved 99\% test coverage using TDD with XUnit and MSpec, reducing production defects by 30\%.}
%     \resumeSubHeadingListEnd

%   \resumeSubheading
%     {Central Biometric Verification Monitoring Platform (CBVMP) (2018 -- 2020)}{}
%     {Synesis IT PLC. Dhaka, Bangladesh}{}
%     \resumeSubHeadingList
%       \resumeItem{Developed a WSIS Award-winning platform using Java, Servlet, and Oracle, enabling biometric verification for 100M+ SIM/MSISDN holders.}
%     \resumeSubHeadingListEnd

%   \resumeSubheading
%     {e-TIN and e-TIN Web API (2018 -- 2020)}{}
%     {Synesis IT PLC. Dhaka, Bangladesh}{}
%     \resumeSubHeadingList
%       \resumeItem{Built e-TIN solutions and APIs using ASP.NET Core and SQL Server, integrating with government stakeholders to enhance tax compliance.}
%     \resumeSubHeadingListEnd
% \resumeSubHeadingListEnd

% \section{LEADERSHIP \& MANAGEMENT}
% \resumeSubHeadingList
%   % \resumeItem{Led engineering teams of up to 8 engineers, aligning technical delivery with product roadmaps and business goals.}
%   \resumeItem{Provided technical direction and engineering governance for backend platform development, aligning system architecture with long-term product strategy.}
%   \resumeItem{Managed Agile/Scrum (sprint planning, backlog grooming, retrospectives) using Jira and Azure DevOps.}
%   \resumeItem{Owned CI/CD and release processes in Azure DevOps — automated deployments, release gates and rollback procedures.}
%   \resumeItem{Defined and enforced quality standards (TDD, unit tests, code reviews, architecture reviews) for features, APIs and integrations.}
%   \resumeItem{Recruited, onboarded and mentored developers via 1:1s, pair programming and technical workshops to accelerate ramp-up.}
%   \resumeItem{Implemented observability and incident response (ELK/Kibana, logging, runbooks) and integrated RBAC/GDPR checks into the SDLC.}
% \resumeSubHeadingListEnd

\section{LEADERSHIP \& MANAGEMENT}
\resumeSubHeadingList
  \resumeItem{Provided technical leadership across backend platform development, guiding architecture decisions, engineering standards, and scalable system design aligned with long-term product strategy.}
  \resumeItem{Led cross-functional delivery across commerce and warehouse domains, combining hands-on backend development with team mentorship and technical oversight.}
  \resumeItem{Designed and maintained CI/CD pipelines in Azure DevOps, enabling automated deployments, release governance, and production reliability.}
  \resumeItem{Established engineering best practices including Clean Architecture, CQRS, TDD, code reviews, and secure API design (JWT, RBAC) across distributed microservices.}
  \resumeItem{Mentored engineers through architectural guidance, pair programming, and technical workshops while contributing directly to backend feature delivery.}
  \resumeItem{Implemented observability strategies (ELK, logging, monitoring) and integrated security and compliance practices into the software development lifecycle.}
\resumeSubHeadingListEnd

% \section{SOFT SKILLS}
% \resumeSubHeadingList
%   \resumeItem{Effective communication with technical and non-technical stakeholders to drive project success.}
%   \resumeItem{Strategic problem-solving and decision-making in high-pressure environments.}
%   \resumeItem{Team collaboration and conflict resolution to ensure cohesive project execution.}
% \resumeSubHeadingListEnd

\section{EDUCATION}
\resumeSubHeadingList
  \resumeSubheading
    {M.Sc. in Computer Science and Engineering (Jan 2018 -- Jun 2019)}{}
    {Jahangirnagar University, Dhaka, Bangladesh}{}
    \resumeItem{Research Topic: Sales forecasting using time series analysis}
  \resumeSubheading
    {B.Sc. in Computer Science (May 2013 -- Dec 2016)}{}
    {American International University-Bangladesh (AIUB), Dhaka, Bangladesh}{}
    \resumeItem{Research Topic: Human health monitoring system using Wireless Sensor Body Area Network (WSBAN)}
\resumeSubHeadingListEnd

\section{AWARDS}
\resumeSubHeadingList
  \resumeItem{World Summit on Information Society (WSIS) Award 2021 -- Central Biometric Verification Monitoring Platform (CBVMP), Action Line C5 category.}
\resumeSubHeadingListEnd

% \section{CERTIFICATIONS}
% \resumeSubHeadingList
%   \resumeItem{SAP Essential Training – LinkedIn Learning (Completion Certificate)}
% \resumeSubHeadingListEnd

\end{document}